Spatial modelling of the two-party preferred vote in Australian federal elections: 2001--2016

### 2019-04-01 draft-paper.tex
Moved functions to separate file and styled all code

\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{unicode-math}
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
\usepackage[unicode=true]{hyperref}
\hypersetup{
            pdftitle={Spatial modelling of the electoral two-party preferred vote in Australia. A study of federal elections between 2001 and 2016 via the eechidna R package.},
            pdfkeywords={federal election, Census, Australia, spatial modelling, imputation, socio-demographics, electorates, R, eechidna},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{geometry}
\geometry{left=2.5cm,right=2.5cm,top=2.5cm,bottom=2.5cm}
\usepackage[style=authoryear-comp,]{biblatex}
\addbibresource{references.bib}
\usepackage{longtable,booktabs}
% Fix footnotes in tables (requires footnote package)
\IfFileExists{footnote.sty}{\usepackage{footnote}\makesavenoteenv{long table}}{}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}

@@

\title{Spatial modelling of the electoral two-party preferred vote in Australia. A study of federal elections between 2001 and 2016 via the \texttt{eechidna} \texttt{R} package.}

@@

\author{Jeremy~Forbes, Di~Cook, Rob~Hyndman}
\addresses{\textbf{Jeremy Forbes}\newline
Monash University\newline Melbourne, Australia
\newline{Email: \href{mailto:jeremy.forbes@monash.edu}{\nolinkurl{jeremy.forbes@monash.edu}}}\newline Corresponding author\\[1cm]
\textbf{Di Cook}\newline
Monash University\newline Melbourne, Australia
\\[1cm]
\textbf{Rob Hyndman}\newline
Monash University\newline Melbourne, Australia
\\[1cm]
}

>>>>

\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{unicode-math}
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
\usepackage[unicode=true]{hyperref}
\hypersetup{
            pdftitle={Spatial modelling of the two-party preferred vote in Australian federal elections: 2001--2016},
            pdfkeywords={federal election, Census, Australia, spatial modelling, imputation, socio-demographics, electorates, R, eechidna},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{geometry}
\geometry{left=2.5cm,right=2.5cm,top=2.5cm,bottom=2.5cm}
\usepackage[style=authoryear-comp,]{biblatex}
\addbibresource{references.bib}
\usepackage{longtable,booktabs}
% Fix footnotes in tables (requires footnote package)
\IfFileExists{footnote.sty}{\usepackage{footnote}\makesavenoteenv{long table}}{}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}

@@

\title{Spatial modelling of the two-party preferred vote in Australian federal elections: 2001--2016}

@@

\author{Jeremy~Forbes, Di~Cook, Rob J~Hyndman}
\addresses{\textbf{Jeremy Forbes}\newline
Monash University\newline Melbourne, Australia
\newline{Email: \href{mailto:jeremy.forbes@monash.edu}{\nolinkurl{jeremy.forbes@monash.edu}}}\newline Corresponding author\\[1cm]
\textbf{Di Cook}\newline
Monash University\newline Melbourne, Australia
\\[1cm]
\textbf{Rob J Hyndman}\newline
Monash University\newline Melbourne, Australia
\\[1cm]
}
